### 2015-05-27 writing/SNLI paper/entailment_eval.tex
Misc updates.

The word embeddings for all of the moedels are initialized the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

>>>>

The word embeddings for all of the models are initialized the 300d reference GloVe vectors (840B token version, \citealt{pennington2014glove}) and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 300d embeddings into the lower-dimensional phrase and sentence embedding space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.
